---
title: "Mass Spectrometry Analysis for Toxins"
author: "Daniel Vogel"
date: '2022-11-18'
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library( knitr )
```

## Description

This poster examines a data set which was created by a Mass Spectrometry(MS) analysis of a sample.
The MS data has been processed by PEAKS DeNovo Assembly to determine the peptides which are likely contained in the sample.
By matching these peptides against a database, it should be possible to determine the contents of the sample and find that the toxin 
Ricinus communis is contained in the sample.



## About this data

- Output from PEAKS DeNovo assembly software
- Sample contains Ricinus communis (castor bean)
- Peptide column contains Amino Acid Sequence of Peptides
- 5798 rows indicate 5798 peptides

## Peptides from Sample and Organisms
\scriptsize
```{r peaks, echo = FALSE}
peaks <- read.csv( "/home/danvogel/R/Capstone/poster/denovo.ricin.555510.csv")
#summary( peaks )
sample_peaks <- head( peaks[c("Peptide","Denovo.Score","Tag.Length","m.z","Mass")] )
knitr::kable( sample_peaks,  caption="PEAKS Sample showing a few of the 5798 peptides found in the sample, their length, mass to charge ratio (m.z.) and Atomic Mass.")
```



```{r organisms, echo = FALSE }
organisms <- read.csv("/home/danvogel/R/Capstone/poster/sample_organisms.csv")
# organisms$common <- c("cow","clementine orange","oyster","castor bean","bacteria")
# organism_table <- organisms[c(1,6,2,3,4,5)]
# write.csv( organism_table, "/home/danvogel/R/Capstone/poster/sample_organisms.csv")
knitr::kable( organisms, caption="Organisms and how many Proteins and Peptides they contain." )


```
\normalsize



